\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-02-14 eg6-letters/NIM/EG6_RTPC_NIM.tex
quick edits, incomplete, just commit it for now

\section{TPC technology} \label{prev_tpc}
In the late 1970s, David R. Nygren presented the concept of the Time Projection 
Chambers (TPCs) as a new tool to track charged particles based on combining 
electric and magnetic fields within a sensitive gas volume. The ionized 
electrons are collected by a position-sensitive electron collection system.  
Later in 1997, F.~Sauli introduced the Gas Electron Multiplier (GEM) as an 
effective gas-gain element to improve the tracking efficiency of the TPCs 
\ref{gem_sauli}. Nowadays, the TPCs are widely used in physics experiments, 
such as high-energy physics (ALEPH, DELPHI), heavy-ion physics (STAR, ALICE) 
and rare-event searches (XENON, NEXT).

@@

\section{CLAS-EG6 RTPC design} \label{sec_design}
The design of CLAS-EG6 RTPC has been chosen according to physics and 
experimental considerations. At 6 GeV incident electron beam energy, the recoil 
$^{4}$He nuclei, from the coherent DVCS channel, have an average momentum (per 
charge) around 125 MeV/c, while the "standard" CLAS detects charged particles 
with a threshold of 250 MeV/c. On the experimental site, the chosen design has 
to fit within the available space inside a 5 Tesla Solenoid magnet that 
surrounds the target \cite{Hyon-suk}. Figure \ref{fig:RTPC2} shows an 
experimental view of the RTPC before being inserted into the solenoid.

The CLAS-EG6 RTPC is a 200~mm long with a 150~mm diameter TPC. While a charged 
particle traverses a gas-sensitive volume, the ionized electrons are released 
and drift, under the effect of an applied electromagnetic field, outward 
perpendicularly to the beam direction. These electrons are then amplified by 
three layers of GEMs and detected by a curved readout system on the external 
shell as can be seen in the figure~\ref{fig:RTPC_1_4}. As for CLAS-BoNuS, the 
EG6-RTPC has two detection halves but unlike BoNuS they are part of a single 
chamber. Each half has independent GEM amplification systems that cover around 
80\% of the azimuthal angle.

@@

The sources of these effects were not determined, but rejection techniques allowed to reconstruct 10\% more good tracks with no significant loss and recover 70 channels that were previously ignored due to high noise levels.

>>>>

\section{TPC technology} \label{prev_tpc}
In the late 1970s, David R. Nygren presented the concept of the Time Projection 
Chambers (TPCs) as a new tool to track charged particles based on combining 
electric and magnetic fields within a sensitive gas volume. The ionized 
electrons are collected by a position-sensitive electron collection system.  
Later in 1997, F.~Sauli introduced the Gas Electron Multiplier (GEM) as an 
effective gas-gain element to improve the tracking efficiency of the TPCs 
\ref{gem_sauli}. Presently, TPCs are widely used in physics experiments, 
such as high-energy physics (ALEPH, DELPHI), heavy-ion physics (STAR, ALICE) 
and rare-event searches (XENON, NEXT).

@@

\section{CLAS-EG6 RTPC design} \label{sec_design}
The design of CLAS-EG6 RTPC has been chosen according to physics and 
experimental requirements.  At 6 GeV incident electron beam energy, the recoil 
$^{4}$He nuclei from coherent DVCS have an average momentum (per 
charge) around 125 MeV/c, while the ``standard'' CLAS detects charged particles 
above a threshold of 250 MeV/c. The chosen design also has 
to fit within the available space inside a 5 Tesla Solenoid magnet
surrounding the target \cite{Hyon-suk}. Figure \ref{fig:RTPC2} shows a photograph of the RTPC before being inserted into the solenoid.

The CLAS-EG6 RTPC is a 200~mm long cylinder with a diameter of 150~mm. While a charged 
particle traverses the sensitive gas volume, ionized electrons are released 
and drift, under the effect of an applied electromagnetic field, outward 
perpendicularly to the beam direction. These electrons are then amplified by 
three layers of GEMs and detected by a curved readout system on the external 
shell as can be seen in the figure~\ref{fig:RTPC_1_4}. As for CLAS-BoNuS, the 
EG6-RTPC has two detection halves but unlike BoNuS they are part of a single 
chamber. Each half has independent GEM amplification systems that cover around 
80\% of the azimuthal angle.

@@

The sources of these effects were not determined, but rejection techniques allowed to reconstruct 10\% more good tracks, with no significant loss, and recover 70 channels that were previously ignored due to excessive noise levels.
